### 2021-04-30 submission.tex
" added previous submission work

%%
%% This is file `sample-acmtog.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmtog')
%%
%% IMPORTANT NOTICE:
%%
%% For the copyright see the source file.
%%
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmtog.tex.
%%
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%%
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[acmtog]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This infrmation is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2021}
\acmYear{2021}
%%\acmDOI{10.1145/1122445.1122456}

%%
%% These commands are for a JOURNAL article.
%%\acmJournal{TOG}
%%\acmVolume{37}
%%\acmNumber{4}
%%\acmArticle{111}
%%\acmMonth{8}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{The Importance of Affective States in Privacy Calculus}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Thibault Irissou}
\affiliation{%
  \institution{Oberlin College}
  \city{Oberlin}
  \country{USA}}
\email{tirissou@oberlin.edu}

\author{Tara Bobinac}
\affiliation{%
  \institution{Oberlin College}
  \city{Oberlin}
  \country{USA}}
\email{tbobinac@oberlin.edu}

\author{Julia Cornell}
\affiliation{%
  \institution{Oberlin College}
  \city{Oberlin}
  \country{USA}}
\email{jcornel2@oberlin.edu}

\author{Riley Chinburg}
\affiliation{%
  \institution{Oberlin College}
  \city{Oberlin}
  \country{USA}}
\email{rchinbur@oberlin.edu}

\graphicspath{ {../images/} }

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Irissou, Bobinac, Chinburg, and Cornell}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
    Research historically understates the importance of affective states within privacy calculus frameworks. However, positive and negative affective states are critical in shaping human behavior. We aim to explore whether positive or negative affect more strongly reinforces privacy conscious behavior.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
%%\begin{CCSXML}
%%<ccs2012>
%% <concept>
%%  <concept_id>10010520.10010553.10010562</concept_id>
%%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%%  <concept_significance>500</concept_significance>
%% </concept>
%% <concept>
%%  <concept_id>10010520.10010575.10010755</concept_id>
%%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
%%  <concept_significance>300</concept_significance>
%% </concept>
%% <concept>
%%  <concept_id>10010520.10010553.10010554</concept_id>
%%  <concept_desc>Computer systems organization~Robotics</concept_desc>
%%  <concept_significance>100</concept_significance>
%% </concept>
%% <concept>
%%  <concept_id>10003033.10003083.10003095</concept_id>
%%  <concept_desc>Networks~Network reliability</concept_desc>
%%  <concept_significance>100</concept_significance>
%% </concept>
%%</ccs2012>
%%\end{CCSXML}
%%
%%\ccsdesc[500]{Computer systems organization~Embedded systems}
%%\ccsdesc[300]{Computer systems organization~Redundancy}
%%\ccsdesc{Computer systems organization~Robotics}
%%\ccsdesc[100]{Networks~Network reliability}
%%

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
%%\keywords{datasets, neural networks, gaze detection, text tagging}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}

Privacy literacy does not necessarily translate into privacy conscious behavior — the great privacy paradox. To describe this seemingly irrational decision-making process, many studies have explored different models of this privacy calculus \cite{Kehr2015}\cite{Jian2013}. These privacy-infringing decisions despite purported privacy concerns may result in negative affective states such as guilt and shame. \\

Question 1: To what extent are guilt or shame the result of privacy infringing decision-making? Is there a correlation between the privacy literacy of an individual and the amount of guilt/shame?

Hypothesis: We believe that guilt and shame will be felt in these situations. We hypothesize that the privacy literacy of an individual will positively correlate with the extent of these negative affective states. \\

Question 2: Does engaging in privacy-preserving behavior result in positive affective states?

Hypothesis 2: We predict that such affectives states will not correlate that strongly with privacy preserving behavior. \\

Question 3: Do these affectives states motivate people to adopt more privacy-preserving behavior?

Hypothesis 3: We predict that both negative affective states are not effective and that positive affective states are effective at motivating such behavior.

\section{Related Works}
\subsection{Privacy paradox, privacy calculus and affects}
The privacy paradox’s existence is for certain, as Barth and de Jong establish in their 2017 literature review. Contextual and environmental circumstances impact the rationality of decision-making, especially online. Studies demonstrate that irrationality in decisions-making regarding privacy is not necessarily circumvented through privacy literacy. \cite{Barth2017}

Some research took the direction of looking at privacy-preserving behavior as being the irrational decision [Cohen]. However, much recent literature assumes that decisions being made are rational insomuch as there is a level of privacy calculus that individuals perform when assessing the risks and rewards of disclosing information or violating their privacy \cite{Kehr2015}\cite{Jian2013}. Affect and affective states (emotions and moods) have been included in recent models of privacy calculus. These frameworks provide the basis for how we conceptualize affective impact on decision making regarding privacy.

\subsection{Negative affective states}
Teroni and Deonna explore in their paper the differentiation of shame and guilt. Their distinctions are the foundation for how we conceptualize negative affective states. We use the questionnaire as detailed in \cite{Rusch2007} as a model for how we build our survey.
\subsection{Positive affective states and Privacy}
Research places importance on the perceived social benefits that come from self-disclosure of information online in synchronous interactive environments\cite{Jian2013}. Such perception of benefits generates positive affective states from such divulsion of information.

In line with the investigation of positive affective states as a motivating factor in behavior shaping \cite{Taneja2014}, we are interested in how positive affective states as a result to making privacy-conscious and privacy-preserving decisions correlate with frequency of such decision-making.

\section{Methodology}
This is a mixed methods study. Surveys are sent out first to find correlations between privacy preserving behavior and the affective states that reinforce them to varying success. Interviews will be conducted with respondents from the survey who want to participate.
\pagebreak
\subsection{Questionnaires}
\nopagebreak The survey is designed to answer:
\begin{itemize}
    \item What privacy protecting behavior respondents actively engage in (from a list of common ones),
    \item How regular and consistent this behavior is
    \item The extent to which respondents feel good or bad when they engage in privacy-protective behavior
    \item The extent to which respondents feel good or bad when they do not engage in privacy-protective behavior
\end{itemize}

\noindent The survey was modeled after multiple established surveys:
\begin{itemize}
    \item Surveys to gauge privacy perception and behavior
    \item Use established questionnaires for measuring negative affects \cite{Rusch2007}
    \item Design questions with best practices for digital methodology in mind \cite{Hampton2017}
\end{itemize}

Quantitative data is analyzed to find correlations between behavior and affect.
\subsection{Interviews}
Findings in the quantitative data will be used by interviewers to help guide interviewees through semi-structured interviews. The objective of the interviews is to \textbf{a)} collect detailed descriptions of the affective states that are experienced before, during, and after engaging in privacy-related behavior, and \textbf{b)} explore the extent to which privacy-related behavior is shaped by the affective states surrounding them. Prior to addressing these, the interviewer will establish what the interviewee's privacy-related habits are and the extent of their knowledge about privacy. \\

The main guiding questions for the interviews are as follow:\\

\textbf{QUESTION 1}: How private and confidential is your information when you’re online? Are there certain activities that are riskier/safer than others?

\textbf{QUESTION 2}: Do you take any protective measures when using the internet? Why or why not?

\textbf{QUESTION 3}: How does the way that you currently browse the internet make you feel in regards to how secure you believe your information to be?

\section{Findings}
\subsection{Survey}
67 responses were collected from people over the age of 18. Respondents were primarily  college students, of which a majority are enrolled at Oberlin College.

\includegraphics[width=0.5\textwidth]{concerns}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{biblio}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\end{document}
\endinput
%%
%% End of file `sample-acmtog.tex'.

### 2021-04-30 submission.tex
references included

@@
 Privacy literacy does not necessarily translate into privacy conscious behavior — the great privacy paradox.
-To describe this seemingly irrational decision-making process, many studies have explored different models of this privacy calculus \cite{Kehr2015}\cite{Jian2013}.
+To describe this seemingly irrational decision-making process, many studies have explored different models of this privacy calculus \cite{Kehr2015} \cite{Jian2013}.
 These privacy-infringing decisions despite purported privacy concerns may result in negative affective states such as guilt and shame.

### 2021-05-01 submission.tex
reformatted

@@
 %% These commands are for a JOURNAL article.
-%%\acmJournal{TOG}
-%%\acmVolume{37}
-%%\acmNumber{4}
-%%\acmArticle{111}
-%%\acmMonth{8}
+\acmJournal{TOG}
+\acmVolume{69}
+\acmNumber{420}
+\acmArticle{314159}
+\acmMonth{5}
 
@@
 
-Privacy literacy does not necessarily translate into privacy conscious behavior — the great privacy paradox.
-To describe this seemingly irrational decision-making process, many studies have explored different models of this privacy calculus \cite{Kehr2015} \cite{Jian2013}.
-These privacy-infringing decisions despite purported privacy concerns may result in negative affective states such as guilt and shame.
-\\
+Privacy literacy does not necessarily translate into privacy conscious behavior
+— the great privacy paradox. To describe this seemingly irrational
+decision-making process, many studies have explored different models of this
+privacy calculus \cite{Kehr2015} \cite{Jian2013}. These privacy-infringing
+decisions despite purported privacy concerns may result in negative affective
+states such as guilt and shame. \\
 
-Question 1: To what extent are guilt or shame the result of privacy infringing decision-making? Is there a correlation between the privacy literacy of an individual and the amount of guilt/shame?
+Question 1: To what extent are guilt or shame the result of privacy infringing
+decision-making? Is there a correlation between the privacy literacy of an
+individual and the amount of guilt/shame?
 
-Hypothesis: We believe that guilt and shame will be felt in these situations.
-We hypothesize that the privacy literacy of an individual will positively correlate with the extent of these negative affective states.
-\\
+Hypothesis: We believe that guilt and shame will be felt in these situations. We
+hypothesize that the privacy literacy of an individual will positively correlate
+with the extent of these negative affective states. \\
 
-Question 2: Does engaging in privacy-preserving behavior result in positive affective states?
+Question 2: Does engaging in privacy-preserving behavior result in positive
+affective states?
 
-Hypothesis 2: We predict that such affectives states will not correlate that strongly with privacy preserving behavior. \\
+Hypothesis 2: We predict that such affectives states will not correlate that
+strongly with privacy preserving behavior. \\
 
-Question 3: Do these affectives states motivate people to adopt more privacy-preserving behavior?
+Question 3: Do these affectives states motivate people to adopt more
+privacy-preserving behavior?
 
-Hypothesis 3: We predict that both negative affective states are not effective and that positive affective states are effective at motivating such behavior.
+Hypothesis 3: We predict that both negative affective states are not effective
+and that positive affective states are effective at motivating such behavior.
 
@@
 \subsection{Privacy paradox, privacy calculus and affects}
-The privacy paradox’s existence is for certain, as Barth and de Jong establish in their 2017 literature review.
-Contextual and environmental circumstances impact the rationality of decision-making, especially online.
-Studies demonstrate that irrationality in decisions-making regarding privacy is not necessarily circumvented through privacy literacy.
-\cite{Barth2017}
+The privacy paradox’s existence is for certain, as Barth and de Jong establish
+in their 2017 literature review. Contextual and environmental circumstances
+impact the rationality of decision-making, especially online. Studies
+demonstrate that irrationality in decisions-making regarding privacy is not
+necessarily circumvented through privacy literacy. \cite{Barth2017}
 
-Some research took the direction of looking at privacy-preserving behavior as being the irrational decision [Cohen].
-However, much recent literature assumes that decisions being made are rational insomuch as there is a level of privacy calculus that individuals perform when assessing the risks and rewards of disclosing information or violating their privacy \cite{Kehr2015}\cite{Jian2013}.
-Affect and affective states (emotions and moods) have been included in recent models of privacy calculus.
-These frameworks provide the basis for how we conceptualize affective impact on decision making regarding privacy.
+Some research took the direction of looking at privacy-preserving behavior as
+being the irrational decision [Cohen]. However, much recent literature assumes
+that decisions being made are rational insomuch as there is a level of privacy
+calculus that individuals perform when assessing the risks and rewards of
+disclosing information or violating their privacy
+\cite{Kehr2015}\cite{Jian2013}. Affect and affective states (emotions and moods)
+have been included in recent models of privacy calculus. These frameworks
+provide the basis for how we conceptualize affective impact on decision making
+regarding privacy.
 
@@
 Teroni and Deonna explore in their paper the differentiation of shame and guilt.
-Their distinctions are the foundation for how we conceptualize negative affective states.
-We use the questionnaire as detailed in \cite{Rusch2007} as a model for how we build our survey.
+Their distinctions are the foundation for how we conceptualize negative
+affective states. We use the questionnaire as detailed in \cite{Rusch2007} as a
+model for how we build our survey.
 \subsection{Positive affective states and Privacy}
-Research places importance on the perceived social benefits that come from self-disclosure of information online in synchronous interactive environments\cite{Jian2013}.
-Such perception of benefits generates positive affective states from such divulsion of information.
+Research places importance on the perceived social benefits that come from
+self-disclosure of information online in synchronous interactive
+environments\cite{Jian2013}. Such perception of benefits generates positive
+affective states from such divulsion of information.
 
-In line with the investigation of positive affective states as a motivating factor in behavior shaping \cite{Taneja2014}, we are interested in how positive affective states as a result to making privacy-conscious and privacy-preserving decisions correlate with frequency of such decision-making.
+In line with the investigation of positive affective states as a motivating
+factor in behavior shaping \cite{Taneja2014}, we are interested in how positive
+affective states as a result to making privacy-conscious and privacy-preserving
+decisions correlate with frequency of such decision-making.
 
 \section{Methodology}
-This is a mixed methods study.
-Surveys are sent out first to find correlations between privacy preserving behavior and the affective states that reinforce them to varying success.
-Interviews will be conducted with respondents from the survey who want to participate.
-\pagebreak
+This is a mixed methods study. Surveys are sent out first to find correlations
+between privacy preserving behavior and the affective states that reinforce them
+to varying success. Interviews will be conducted with respondents from the
+survey who want to participate.
 \subsection{Questionnaires}
@@
 \begin{itemize}
-    \item What privacy protecting behavior respondents actively engage in (from a list of common ones),
+    \item What privacy protecting behavior respondents actively engage in (from
+	a list of common ones),
     \item How regular and consistent this behavior is
-    \item The extent to which respondents feel good or bad when they engage in privacy-protective behavior
-    \item The extent to which respondents feel good or bad when they do not engage in privacy-protective behavior
+    \item The extent to which respondents feel good or bad when they engage in
+	privacy-protective behavior
+    \item The extent to which respondents feel good or bad when they do not
+	engage in privacy-protective behavior
 \end{itemize}
@@
     \item Surveys to gauge privacy perception and behavior
-    \item Use established questionnaires for measuring negative affects \cite{Rusch2007}
-    \item Design questions with best practices for digital methodology in mind \cite{Hampton2017}
+    \item Use established questionnaires for measuring negative affects
+	\cite{Rusch2007}
+    \item Design questions with best practices for digital methodology in mind
+	\cite{Hampton2017}
 \end{itemize}
@@
 \subsection{Interviews}
-Findings in the quantitative data will be used by interviewers to help guide interviewees through semi-structured interviews.
-The objective of the interviews is to \textbf{a)} collect detailed descriptions of the affective states that are experienced before, during, and after engaging in privacy-related behavior, and \textbf{b)} explore the extent to which privacy-related behavior is shaped by the affective states surrounding them.
-Prior to addressing these, the interviewer will establish what the interviewee's privacy-related habits are and the extent of their knowledge about privacy.
-\\
+Findings in the quantitative data will be used by interviewers to help guide
+interviewees through semi-structured interviews. The objective of the interviews
+is to \textbf{a)} collect detailed descriptions of the affective states that are
+experienced before, during, and after engaging in privacy-related behavior, and
+\textbf{b)} explore the extent to which privacy-related behavior is shaped by
+the affective states surrounding them. Prior to addressing these, the
+interviewer will establish what the interviewee's privacy-related habits are and
+the extent of their knowledge about privacy.
 
@@
 
-\textbf{QUESTION 1}: How private and confidential is your information when you’re online? Are there certain activities that are riskier/safer than others?
+\textbf{QUESTION 1}: How private and confidential is your information when
+you’re online? Are there certain activities that are riskier/safer than others?
 
-\textbf{QUESTION 2}: Do you take any protective measures when using the internet? Why or why not?
+\textbf{QUESTION 2}: Do you take any protective measures when using the
+internet? Why or why not?
 
-\textbf{QUESTION 3}: How does the way that you currently browse the internet make you feel in regards to how secure you believe your information to be?
+\textbf{QUESTION 3}: How does the way that you currently browse the internet
+make you feel in regards to how secure you believe your information to be?
 
@@
 \subsection{Survey}
-67 responses were collected from people over the age of 18. Respondents were primarily  college students, of which a majority are enrolled at Oberlin College.
+67 responses were collected from people over the age of 18. Respondents were
+primarily  college students, of which a majority are enrolled at Oberlin
+College.
 
+\subsection{Respondents' Privacy Concerns}
+On average, respondents reported two privacy concerns of the five that were
+suggested. The most common concern---password security---was three times as
+popular than the least common concern---email tracking.
+
+Fig. \ref{Univariate Distribution Respondent Concerns} presents the frequency
+distribution of all five possible concerns.
+
+\begin{figure}[H]
     \includegraphics[width=0.5\textwidth]{concerns}
+    \caption{Frequency distribution for respondents' self-reported privacy
+    concerns}
+    \label{Univariate Distribution Respondent Concerns}
+\end{figure}
 
-%%
 %% The next two lines define the bibliography style to be used, and
@@
 
-%%
 %% If your work has an appendix, this is the place to put it.

### 2021-05-01 submission.tex
Findings for Ad Tracking added

@@
 
+\subsection{Ad Tracking}
+A strong relationship exists such that \emph{the better an individual feels when
+they delete cookies, the more frequently they delete them}. This was determined
+by obtaining the gamma correlation value of magnitude .821 (p<.01,**) between
+ordinal values for ``How often do you delete cookies on the device you most
+regularly use for browsing?'' and ``How do you feel when you delete cookies?''.
+Despite the strength of the relationship, the Chi-Square p-value of .178
+indicates that the null hypothesis cannot be ruled out.
+
+\subsection{Privacy and Social Media}
+
+\begin{figure}[H]
+    \includegraphics[width=0.5\textwidth]{univariate social media practices}
+    \caption{Respondents' actual privacy practices regarding on social media.
+	Only respondents who indicated concern about social media privacy were
+	asked to answer this question.}
+    \label{Univariate Distribution Respondent Concerns}
+\end{figure}
 %% The next two lines define the bibliography style to be used, and

### 2021-05-01 submission.tex
Findings for VPN usage

@@
 \end{figure}
+
+\subsection{VPN Usage}
+We exclude from our analyses one respondent who did not know what a VPN was.
+
+Strong relationship between \emph{how an individual feels when using a VPN and
+whether they use one}, with a gamma value of .786. Relatively significant
+relationship (p=.169) given sample size.  Relatively significant Chi-Square
+(p=.107), despite not ruling out null hypothesis conclusively.
+
+Perfect correlation between \emph{how an individual feels while setting up a
+VPN, and whether they use one}. Relatively significant relationship (p=.169)
+given sample size. Relatively significant Chi-Square (p=.211), despite not
+ruling out null hypothesis conclusively.
+
+With a gamma value of .973, there eists a near perfect relationship between
+\emph{how an individual feels after setting up a VPN and how they feel when
+their device is using a VPN}. This relationship is highly significant
+(p<.001,***), and the chi-square test of significance rules out the null
+hypothesis (p<.001,***).
+
+A perfect inverse relationship exists between \emph{how somebody feels while
+setting up a VPN and how they feel if their device is not using one}. It is
+relatively significant (p=.139) given the small sample size.  Relatively
+significant Chi-Square (p=.183), despite not ruling out null hypothesis
+conclusively.
+
+\section{Discussion}
+\subsection{Ad Tracking}
+\textbf{TODO}
+The inability to rule out the null hypothesis is likely due to the small sample
+size of 34 respondents who were asked these questions.
+
 %% The next two lines define the bibliography style to be used, and

### 2021-05-02 submission.tex
findings on social media

@@
 
-\subsection{VPN Usage}
+A strong relationship exists between \emph{the proportion of social media for
+which an individual has set up privacy settings and how they feel when they are
+setting up those settings}, with a correlation of magnitude .742. This
+relationship is highly significant (p<.01, **). Despite the a relatively low
+Chi-Square (p=.115), we cannot rule out the null hypothesis.
+
+\subsection{ISP Tracking Concerns and VPN Usage}
 We exclude from our analyses one respondent who did not know what a VPN was.

### 2021-05-03 submission.tex
findings for password section

@@
 
+\subsection{Password Security}
+There exists a strong relationship such that \emph{if an individual used the
+same passwords for most of their accounts, they feel worse about it if they use
+some password protective measures}. The gamma value of this relationship is
+.477, with p<.05 (*). Despite the strength of the relationship, the Chi-Square
+p-value of .131 indicates that the null hypothesis cannot be ruled out.
+
+There is a strong positive correlation betwen \emph{how an individual feels when
+they reuse an old password, and how they feel if most of their accounts used the
+same password}. The gamma correlation value of .733 is significant (p<.001,***).
+The null hypothesis can be ruled out (Chi-Square p<.01,**).
 \section{Discussion}

### 2021-05-03 submission.tex
relabeling findings for references

@@
 
-\subsection{Respondents' Privacy Concerns}
+\subsection{Privacy Concerns} \label{Privacy Concerns}
 On average, respondents reported two privacy concerns of the five that were
@@
 
-\subsection{Ad Tracking}
+\subsection{Ad Tracking} \label{Ad Tracking}
 A strong relationship exists such that \emph{the better an individual feels when
@@
 
-\subsection{Privacy and Social Media}
+\subsection{Social Media} \label{Social Media}
 
@@
 
-\subsection{ISP Tracking Concerns and VPN Usage}
+\subsection{VPN Usage (ISP Conerns)} \label{VPN Usage}
 We exclude from our analyses one respondent who did not know what a VPN was.

### 2021-05-03 submission.tex
password security rephrase

@@
 
-\subsection{Password Security}
-There exists a strong relationship such that \emph{if an individual used the
-same passwords for most of their accounts, they feel worse about it if they use
-some password protective measures}. The gamma value of this relationship is
-.477, with p<.05 (*). Despite the strength of the relationship, the Chi-Square
-p-value of .131 indicates that the null hypothesis cannot be ruled out.
+\subsection{Password Security} \label{Password Security}
+There exists a strong relationship such that \emph{the worse an individual feels
+if they used the same passwords for most of their accounts, the more likely they
+are to use password protective measures}.  The gamma value of this relationship
+is .477, with p<.05 (*). Despite the strength of the relationship, the
+Chi-Square p-value of .131 indicates that the null hypothesis cannot be ruled
+out.
 

### 2021-05-03 submission.tex
quant discussion

@@
 The null hypothesis can be ruled out (Chi-Square p<.01,**).
+
 \section{Discussion}
-\subsection{Ad Tracking}
-\textbf{TODO}
-The inability to rule out the null hypothesis is likely due to the small sample
-size of 34 respondents who were asked these questions.
+\subsection{Privacy Habits and Affectives States}
+Strong correlations exist between how people feel and their privacy related
+habits. Intuitively, privacy related behavior and habits are comparable to
+housekeeping insomuch as they are not immediately sources of great happiness,
+but they offer long term benefits. Individuals who feel good when they engage in
+privacy conscious behavior tend to practice such behavior more frequently.
+\emph{It is unclear whether the habit itself causes the individual to experience
+more positive affective states, or whether it is the affective states that
+determine whether an individual is likely to form such a habit or not.}
+
+% Should this go into a Further Research section?
+In future research, a behavioral study leveraging regression discontinuity
+design can provide insight as to the directionality of the relationship between
+privacy habits/behavior and affective states.
+
+For nearly all the relationships that were analyzed, it is not possible to rule
+out the null hypothesis due to the survey's insufficient sample size.
 
